Gaze-dependent evidence accumulation predicts multi-alternative risky choice behaviour

### 2021-04-16 manuscript/manuscript_refs-apa.tex
added statement over sample size determination, line numbers, dois, removed annotation fields from references

% Reference management
\usepackage[style=apa,doi=false,url=false,eprint=false]{biblatex}
\addbibresource{references.bib}

% \linenumbers  % uncomment to add line numbers

@@

We recruited 44 participants for the experiment. All participants were required to have normal or corrected to normal vision with soft contact lenses. Participants relying on glasses or hard contact lenses were excluded from participation to ensure good eye tracking quality. Four participants were excluded from the analyses: one due to a computer crash, two due to eye tracking calibration worse than 1.0$\degree$ of visual angle, and one because of misunderstanding task instructions.  The remaining 40 participants (25 female, 15 male) had mean $\pm$ s.d. age 27.2 $\pm$ 4.7. All participants received a base compensation of 8 Euros per hour and could win an additional bonus based on their choices during the experiment (see below). Written informed consent was obtained from all participants prior to the experiment. The experimental procedures were approved by Freie Universität’s ethics committee.

>>>>

% Reference management
\usepackage[style=apa,doi=true,url=false,eprint=false]{biblatex}
\addbibresource{references.bib}

\linenumbers  % uncomment to add line numbers

@@

An effective sample size of 40 was determined for this study based on related eye tracking studies of decision making. In total, we recruited 44 participants for the experiment. All participants were required to have normal or corrected to normal vision with soft contact lenses. Participants relying on glasses or hard contact lenses were excluded from participation to ensure good eye tracking quality. Four participants were excluded from the analyses: one due to a computer crash, two due to eye tracking calibration worse than 1.0$\degree$ of visual angle, and one because of misunderstanding task instructions.  The remaining 40 participants (25 female, 15 male) had mean $\pm$ s.d. age 27.2 $\pm$ 4.7. All participants received a base compensation of 8 Euros per hour and could win an additional bonus based on their choices during the experiment (see below). Written informed consent was obtained from all participants prior to the experiment. The experimental procedures were approved by Freie Universität’s ethics committee.
